KidsAIR: merge health datasets

### 2020-04-06 child_health_data_cleaning.Rmd
health data update, LRTI tracking

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 27 March 2020"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
wmt_medicalvisit_initial <- read_xlsx("Input/WMT/wmt_medicalvisit_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         lethargy = as.character(Lethargy),
         retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         resp_rate = as.numeric(RR),
         heart_rate = as.numeric(HR),
         wheeze = as.character(Wheeze),
         stridor = as.character(Stridor),
         crackles = as.character(Crackles),
         sp02 = as.numeric(SP02),
         hr_sp02 = as.numeric(HRPulseOx),
         referred = as.character(Referred),
         med_visit_notes = as.character(Notes)) %>% 
  select(home_winter_id:med_visit_notes) %>% 
  replace_with_na_all(condition = ~.x == -999)

nn_medicalvisit_initial <- read_xlsx("Input/NN/nn_medicalvisit_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         lethargy = as.character(Lethargy),
         retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         resp_rate = as.numeric(RR),
         heart_rate = as.numeric(HR),
         wheeze = as.character(Wheeze),
         stridor = as.character(Stridor),
         crackles = as.character(Crackles),
         sp02 = as.numeric(SP02),
         hr_sp02 = as.numeric(HRPulseOx),
         referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  select(home_winter_id:med_visit_notes) %>% 
  replace_with_na_all(condition = ~.x == -999)

ak_medicalvisit_initial <- read_xlsx("Input/AK/ak_medicalvisit_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         lethargy = as.character(Lethargy),
         retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         resp_rate = as.numeric(RR),
         heart_rate = as.numeric(HR),
         wheeze = as.character(Wheeze),
         stridor = as.character(Stridor),
         crackles = as.character(Crackles),
         sp02 = as.numeric(SP02),
         hr_sp02 = as.numeric(HRPulseOx),
         referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  select(home_winter_id:med_visit_notes) %>% 
  replace_with_na_all(condition = ~.x == -999)

@@

# Load and merge files from different locations
```{r}
wmt_childhomewinter_initial <- read_xlsx("Input/WMT/wmt_childhomewinter_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         dr_relook = DrRelook,
         ari_status = as.character(Status),
         symptom_free_date = ymd(SymptomFreeDate),
         csq_duedate = ymd(CSQDueDate),
         csq_date = ymd(CSQDate),
         csq_time = as.character(CSQTime),
         dr_comments = as.character(DrComments),
         dr_history = as.character(DrHistory),
         notify_parents = as.character(NotifyParents),
         notes_to_parents = as.character(NotesToParents),
         any_ari = as.character(AnyARI),
         ari_comments = as.character(WinterARIComments)) %>% 
  select(home_winter_id:ari_comments)

@@

# Load and merge files from different locations
```{r}
wmt_csq_initial <- read_xlsx("Input/WMT/wmt_csq_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         csq_date = ymd(Date),
         sick_2_weeks = as.character(Illin2Weeks),
         sick = as.character(Sick),
         ari = as.character(ARI),
         still_sick = as.character(StillSick),
         first_symptom_date = ymd(FirstSymptomDate),
         see_dr = as.character(SeeDr),
         dr_diagnosis = as.character(DrDiagnosis),
         new_meds = as.character(NewMeds),
         fever = as.character(Fever),
         temp = as.numeric(Temperature),
         rapid_breathing = as.character(RapidBreathing),
         difficult_breathing = as.character(DifficultBreathing),
         noisy_breathing = as.character(NoisyBreathing),
         runny_nose = as.character(RunnyNose),
         cough = as.character(Coughing),
         wheeze = as.character(Wheezing),
         symptom_free_date = ymd(SymptomFreeDate),
         comments = as.character(Comments)) %>% 
  select(home_winter_id:comments)

@@

# Load and merge files from different locations
```{r}
wmt_medicalrecords_initial <- read_xlsx("Input/WMT/wmt_medicalrecords_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         visit_date = ymd(VisitDate),
         dr_diagnosis = as.character(DrDiag),
         ari = as.character(ARI),
         comments = as.character(DrComments)) %>% 
  select(home_winter_id:comments)

>>>>

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 6 April 2020"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
wmt_medicalvisit_initial <- read_xlsx("Input/WMT/wmt_medicalvisit_20200227.xlsx") %>% 
  replace_with_na_all(condition = ~.x == -999) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         med_visit_lethargy = as.character(Lethargy),
         med_visit_retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         med_visit_resp_rate = as.numeric(RR),
         med_visit_heart_rate = as.numeric(HR),
         med_visit_wheeze = as.character(Wheeze),
         med_visit_stridor = as.character(Stridor),
         med_visit_crackles = as.character(Crackles),
         med_visit_sp02 = as.numeric(SP02),
         med_visit_hr_sp02 = as.numeric(HRPulseOx),
         med_visit_referred = as.character(Referred),
         med_visit_notes = as.character(Notes)) %>% 
  # gather 3 temperatures to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  group_by(home_winter_id, med_visit_date) %>% 
  mutate(med_visit_mean_temp = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>%
  select(home_winter_id:med_visit_mean_temp)

nn_medicalvisit_initial <- read_xlsx("Input/NN/nn_medicalvisit_20200227.xlsx") %>% 
  replace_with_na_all(condition = ~.x == -999) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         med_visit_lethargy = as.character(Lethargy),
         med_visit_retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         med_visit_resp_rate = as.numeric(RR),
         med_visit_heart_rate = as.numeric(HR),
         med_visit_wheeze = as.character(Wheeze),
         med_visit_stridor = as.character(Stridor),
         med_visit_crackles = as.character(Crackles),
         med_visit_sp02 = as.numeric(SP02),
         med_visit_hr_sp02 = as.numeric(HRPulseOx),
         med_visit_referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  # gather 3 temperatures to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  group_by(home_winter_id, med_visit_date) %>% 
  mutate(med_visit_mean_temp = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>%
  select(home_winter_id:med_visit_mean_temp)

ak_medicalvisit_initial <- read_xlsx("Input/AK/ak_medicalvisit_20200227.xlsx") %>% 
  replace_with_na_all(condition = ~.x == -999) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         med_visit_lethargy = as.character(Lethargy),
         med_visit_retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         med_visit_resp_rate = as.numeric(RR),
         med_visit_heart_rate = as.numeric(HR),
         med_visit_wheeze = as.character(Wheeze),
         med_visit_stridor = as.character(Stridor),
         med_visit_crackles = as.character(Crackles),
         med_visit_sp02 = as.numeric(SP02),
         med_visit_hr_sp02 = as.numeric(HRPulseOx),
         med_visit_referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  # gather 3 temperatures to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  group_by(home_winter_id, med_visit_date) %>% 
  mutate(med_visit_mean_temp = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>%
  select(home_winter_id:med_visit_mean_temp)

@@

# Load and merge files from different locations
```{r}
wmt_childhomewinter_initial <- read_xlsx("Input/WMT/wmt_childhomewinter_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         chw_dr_relook = DrRelook,
         chw_ari_status = as.character(Status),
         chw_symptom_free_date = ymd(SymptomFreeDate),
         chw_csq_duedate = ymd(CSQDueDate),
         chw_csq_date = ymd(CSQDate),
         chw_csq_time = as.character(CSQTime),
         chw_dr_comments = as.character(DrComments),
         chw_dr_history = as.character(DrHistory),
         chw_notify_parents = as.character(NotifyParents),
         chw_notes_to_parents = as.character(NotesToParents),
         chw_any_ari = as.character(AnyARI),
         chw_ari_comments = as.character(WinterARIComments)) %>% 
  select(home_winter_id:chw_ari_comments)

@@

# Load and merge files from different locations
```{r}
wmt_csq_initial <- read_xlsx("Input/WMT/wmt_csq_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         csq_date = ymd(Date),
         csq_collect = as.character(HowCollected),
         csq_sick_2_weeks = as.character(Illin2Weeks),
         csq_still_sick = as.character(StillSick),
         csq_first_symptom_date = ymd(FirstSymptomDate),
         csq_symptom_free_date = ymd(SymptomFreeDate),
         csq_miss_work = as.character(MissWork),
         csq_miss_work_days = as.character(DaysMissed),
         csq_see_dr = as.character(SeeDr),
         csq_dr_diagnosis = as.character(DrDiagnosis),
         csq_new_meds = as.character(NewMeds),
         csq_fever_2weeks = as.character(Fever),
         csq_temp_2weeks = as.numeric(Temperature),
         csq_rapid_breathing_2weeks = as.character(RapidBreathing),
         csq_difficult_breathing_2weeks = as.character(DifficultBreathing),
         csq_noisy_breathing_2weeks = as.character(NoisyBreathing),
         csq_runny_nose_2weeks = as.character(RunnyNose),
         csq_cough_2weeks = as.character(Coughing),
         csq_wheeze_2weeks = as.character(Wheezing),
         csq_fever_current = as.character(FeverStill),
         csq_rapid_breathing_current = as.character(RapidBreathingStill),
         csq_difficult_breathing_current = as.character(DifficultBreathingStill),
         csq_noisy_breathing_current = as.character(NoisyBreathingStill),
         csq_runny_nose_current = as.character(RunnyNoseStill),
         csq_cough_current = as.character(CoughingStill),
         csq_wheeze_current = as.character(WheezingStill),
         csq_comments = as.character(Comments)) %>% 
  select(home_winter_id:csq_comments)

@@

# Load and merge files from different locations
```{r}
wmt_medicalrecords_initial <- read_xlsx("Input/WMT/wmt_medicalrecords_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(ARI),
         med_rec_comments = as.character(DrComments)) %>% 
  select(home_winter_id:med_rec_comments)

### 2020-04-06 merge_health_datasets.Rmd
health data update, LRTI tracking

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 27 March 2020"
output: pdf_document
---

@@

# Initial data merge - long format
```{r}
kids_med_visit <- read_rds("Output/kids_med_visit.rds") %>% 
  mutate(visit_date = med_visit_date) %>% 
  rename(wheeze_med_visit = wheeze)

health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  rename(wheeze_csq = wheeze) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_notes) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

child_home_winter <- read_rds("Output/child_home_winter.rds") %>% 
  select(-csq_date, -home_id.x, -home_id.y, -symptom_free_date)

@@

#write_rds(health_merged4, "Output/health_data_merged.rds")
#write_csv(health_merged4, "Output/health_data_merged.csv")
```

>>>>

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 6 April 2020"
output: pdf_document
---

@@

# Initial data merge - long format
```{r}
kids_med_visit <- read_rds("Output/kids_med_visit.rds") %>% 
  mutate(visit_date = med_visit_date)

health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_notes) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

child_home_winter <- read_rds("Output/child_home_winter.rds") %>% 
  select(-home_id.x, -home_id.y, -chw_symptom_free_date)

@@

kids_medical_records <- read_rds("Output/kids_medical_records.rds") %>% 
  select(-visit_date)

health_merged5 <- health_merged4 %>% 
  left_join(kids_medical_records, by = c("area", "home", "home_winter_id", "winter_id", 
                                      "child_id_num", "treatment")) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, sample_date, sampling_day, at_home_location, 
         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:med_rec_comments) %>% 
  ungroup()

#write_rds(health_merged5, "Output/health_data_merged.rds")
#write_csv(health_merged5, "Output/health_data_merged.csv")
```
